|

### 2025-12-03 manuscript/pre_print.qmd
Add Nguo et al (2025) reference

Therefore, to estimate and describe the magnitude of difference in REE between women with and without PCOS, we completed a systematic review and meta-analysis of studies reporting REE in these populations.

>>>>

A recent scoping review has highlighted the inconsistency in research examining energy expenditure in women with PCOS [@nguoExploringPhysiologicalFactors2025]. However, to our knowledge there has been no attempts to systematically review, and quantitatively synthesise via meta-analysis, studies of REE in women with, and without, PCOS. Therefore, to estimate and describe the magnitude of difference in REE between women with and without PCOS, we completed a systematic review and meta-analysis of studies reporting REE in these populations.
